\Large \bf Dynamic Program Dialysis with Lya

### 2020-01-06 paper/draft.tex
Add base transform

\newcommand{\cf}[1]{(\emph{Cf}.\S\ref{#1})}
\newcommand{\sx}[1]{(\S\ref{#1})}
\newcommand{\sys}{{\scshape Lya}\xspace}
\newcommand{\toy}{{\tt lya.js}\xspace}

@@

@@

\begin{table}[t]
\center
\footnotesize
\setlength\tabcolsep{3pt}
\caption{
  \footnotesize{
    \textbf{Language features used and their availability in other languages}.
    Broadly, the requirements of module dialysis can be broken down into to five elementary requirements.
  }
}
\begin{tabular*}{\columnwidth}{l @{\extracolsep{\fill}} llllllll}
\toprule
                                & Lua     & JavaScript  & Ruby   &      &      &      &      &         \\
\midrule
Instrument \ttiny{import}s      &         &             &        &      &      &      &      &         \\
Walk objects                    &         &             &        &      &      &      &      &         \\
Shadow variables                &         &             &        &      &      &      &      &         \\
Wrap values                     &         &             &        &      &      &      &      &         \\
Global names                    &         &             &        &      &      &      &      &         \\
\bottomrule
\end{tabular*}
\label{tab:compatibility}
\vspace{-5mm}
\end{table}

@@

>>>>

\definecolor{cdb}{rgb}{0.37, 0.62, 0.63} % cadet blue

\newcommand{\cf}[1]{(\emph{Cf}.\S\ref{#1})}
\newcommand{\sx}[1]{(\S\ref{#1})}
\newcommand{\tb}[1]{(Tab.\ref{tab:#1})}
\newcommand{\sys}{{\scshape Lya}\xspace}
\newcommand{\toy}{{\tt lya.js}\xspace}

@@

\begin{figure}[t]
\raggedleft 
\includegraphics[width=0.45\textwidth]{./figs/lya_base.pdf}
\caption{
  \textbf{Base transformation.}
  \textmd{
  The algorithm (simplified) is presented in functional style to simplify variable binding; types (object, list, function, and primitive), used for pattern matching, are shown in light {\color{cdb} \emph{turquoise}}~\cf{bt}.
  }
}
\label{fig:base}
\end{figure}

@@

\begin{table}[t]
\center
\footnotesize
\setlength\tabcolsep{3pt}
\caption{
  \footnotesize{
    \textbf{Language features used and their availability in other languages}.
    Broadly, the requirements of module dialysis can be broken down into to five elementary requirements.
  }
}
\begin{tabular*}{\columnwidth}{l @{\extracolsep{\fill}} llllllll}
\toprule
                                & Lua     & JavaScript  & Ruby   &      &      &      &      &         \\
\midrule
Instrument \ttiny{import}s      &         &             &        &      &      &      &      &         \\
Walk objects                    &         &             &        &      &      &      &      &         \\
Shadow variables                &         &             &        &      &      &      &      &         \\
Wrap values                     &         &             &        &      &      &      &      &         \\
Global names                    &         &             &        &      &      &      &      &         \\
\bottomrule
\end{tabular*}
\label{tab:compat}
\vspace{-5mm}
\end{table}

The techniques presented in this paper are applicable to any programming language.
We chose the JavaScript ecosystem to evaluate the feasibility of our approach, primarily because
  (i) it boasts the largest collection of libraries (and number of problems)~\cite{modulecounts} and
	(ii) we had prior experience by writing two systems that make extensive use of dynamic analysis---more sophisticated versions of analyses \fixme{XX} and \fixme{XX}.
In this section, we discuss the requirements for building \sys over other runtime environments.
% FIXME: All these features have to have been discussed earlier

By operating on library boundaries, program dialysis makes use of five key features available in a programming language~\tb{compat}.
All major programming languages can support these five features in a variety of ways, as described below.

First, \sys replaces the implementation of the import statement (\eg \ttt{require});
  this feature is important for compatibility reasons---otherwise developers would have to replace all import statements in a deeply nested tree.
If this is a function (\eg JavaScript, Scheme, Racket \etc) then replacement can be easily achieved by replacing its definition.
If this is a special-keyword statement such as \ttt{import}, this can be achieved by a rewriting rule that replaces import with a special function;
% This is simplified by the fact that the import syntax is trivial.

Second, \sys makes extensive use of weak maps to support to check for equality and, more frequently, for checking for cycles during object traversal (which requires equality).

@@

Other dynamic languages such as Lua, Ruby, and Python conveniently unify module identification with runtime interposition:
% used for performance monitoring and replica construction:
  a single function or function-like operator locates a module, interprets it, and applies transformations before exposing its interface in the caller context.
All these languages offer runtime capabilities such as name (re-)binding, value introspection, name interception, and access interposition.
% Languages such as Smalltalk and Lisp that treat ``everything'' as an object or a  function, need to interpose through object wrappers or function closures, respectively.

Compiled languages such as Haskell, OCaml, and Rust would apply transformations using compile-time metaprogramming facilities.
Examples include templates (\eg Template Haskell) and macro expansions (\eg Rust's macro system).
Such facilities would alleviate the runtime overhead of transformations, improving program startup times;
  however, they would not affect the overhead of contract evaluation, as this is still a runtime operation.
Static type checking could further aid developers by issuing warnings of incompatible privilege settings.
Contrary to OSMLC, there is no need for support from the runtime linker~\cite[\S VII]{breakapp:ndss:2018} because compartments do not execute as separate processes.
